---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

---

googlenlp
---

The googlenlp package provides an R interface to Google's [Cloud Natural Language API](https://cloud.google.com/natural-language/).


### Installation

You can install the development version from GitHub:

```{r eval = FALSE}
devtools::install_github("BrianWeinstein/googlenlp")
```


### Authentication

To use the API, you'll first need to [create a Google Cloud project and enable billing](https://cloud.google.com/natural-language/docs/getting-started), and get an [API key](https://cloud.google.com/natural-language/docs/common/auth).


### Getting started

Load the package and set your API key.
```{r eval = FALSE}
library(googlenlp)

set_api_key("MY_API_KEY")
```

Define the text you'd like to analyze.
```{r eval = TRUE}
my_text <- "Google, headquartered in Mountain View, unveiled the
            new Android phone at the Consumer Electronic Show.
            Sundar Pichai said in his keynote that users love
            their new Android phones."
```

The `annotate_text` function analyzes the text's syntax (sentences and tokens), entities, sentiment, and language.

```{r include = FALSE}
library(googlenlp)
# library(dplyr) # without this, R can't find dplyr::rowwise
set_api_key(readLines("tests/testthat/api_key.txt"))
```

```{r eval = TRUE}
annotate_text(text_body = my_text)
```


